Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2014-10-24 misc/SI_thesis.tex
misc works of paper reading, wo3 raman table etc

@@

@@

A systematic study of optical and electrical properties of \ce{WO3} thin film.\cite{Deb1973} Film density 6.5 \si{g\per cm^3}, substantial porosity. \ce{WO3} become substoichiometric at 1300-1500 K, and evaporate at a composition near \ce{WO_{2.96}}. $K \propor (h\nu - E_g)^2/h\nu$, indicating an allowed band to band transition, and 3.25 eV energy gap determined thereby. Refractive index $\epsilon_{st}$ of thin film \ce{WO3} found at 2.2, lower than that of single crystal value of 2.5; $n$ increases to 4.0 at absorption edge region, with $\alpha$ as high as $10^5$ \si{cm^{-1}}. So the color center can form in a thin layer of 100 nm; its density estimated by the Smakula's Equation:
\[
Nf = 0.89\times10^17\frac{n}{(n^2+2)^2} \alpha d
\]
where $f$ osc strength, n ref index, $\alpha$ in \si{cm^{-1}}, and d is the half width of absorption band. Assuming $f$ = 1, N to be $5\times10^{19}$ \si{cm^3}. 
Narrow conduction band proposed to explain the high energy peak at 4.39 eV and 5.25 eV. Impurity band when the ele wavefuntion overlap, the color center spacing comparable to lattice constant.

@@

raman assign
\begin{table}[htb]
\centering
\caption{Symmetry assignment of \ce{WO3}}\label{tab:woram}
\begin{tabular}{cccc}
\toprule
Raman shift (\si{cm^{-1}}) & Symmetry &  Ref.   & Remarks   \\
\midrule
131(m)   & $B_{2g}$    &           & $T_c$    \ce{WO3} \\
265(m)   & $B_{3g}$    &           & $T_c$    \\
327(m)   & $A_g/B_{1g}$&           & $T_b$   \\
711(s)     & $B_{2g}$    & $\tau$    &          \\
803(vs)     & $A_g$       &           & $R_c$    \\
\midrule
230(m)   & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  \ce{WO3.H2O} \\
380(w)   & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
428(w)   & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
650(s)  & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
816(vs)   & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
946(vw)      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}

vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}

\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Name & Raman Shift (\si{cm^{-1}}) &  Ref   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na4W4O13} & &\\
\ce{Na5W14O44} & & this work
\bottomrule
\end{tabular}
Materials in solid state, 
vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}

@@

Delichere1988coloured states

@@

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$ in unit of \si{\coulomb}\per\cm^2) during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

>>>>

how to show the crystalline TMO is better than amorphous thin film counterparts.

In comparison to oxides thin films, 1D \gls{tmo} nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened. (2) The gap between nanowires always provides channels for fast ion diffusion outside the nanowires. (3) The large surface area to bulk volume ratio of nanowires is desired to improve the overall usage of material, which results in enhanced the contrast between colored and bleached states. Furthermore, doped with certain metals (such as Ti and Ag), the crystalline structure of the TMO nanowires can be modified with enhanced electrochromic properties.\cite{Xiong2008}

@@

soda lime glass. thermal radiative transfer through windows, \cite{Rubin1985} \ce{FeO} absorb infrared, and \ce{Fe2O3} in ultraviolet,

The phase of amplitude reflection coeffs
\[
\phi(\omega) = \frac{1}{2\pi} \int_0^\infty \frac{d\log r}{d\omega'}\log(abs(\frac{\omega' + \omega}{\omega' - \omega}))d\omega'
\]

two python projects available, KKcalc\cite{Watts2014} and hyperSpy. 
http://www1.univap.br/gaa/nkabs-database/data.htm

KK relations in optical materials research. 
\begin{align}
N(\omega) &= [N(-\omega)]^* \\
N(\omega) - 1 &\approx -\frac{\omega_p^2}{2\omega^2}\\
r(\omega) = \frac{N(\omega)-1}{N(\omega)+1} &= \frac{n-1+ik}{n+1+ik}\\
r(\omega) &= |r(\omega)| \exp[i\theta(\omega)]\\
\log r(\omega) &= \log|r(\omega)| + i\theta(\omega)
\end{align}

phase retrieval, 
Principal value:
\[
P\cdot\int_0^\infty f(x)dx = \lim_{\delta\rightarrow 0} (\int_0^{a-\delta} f(x)dx + \int_{a+\delta}^\infty f(x)dx)
\]

Maclaurin methodology, \cite{Rocha2014}. The singularity,

\[
\nu_1, \nu_2, \nu_3, \ldots, \nu_m;\\
k_1,k_2,
\]

\[
n(\nu) = n_0 + 2/\pi \int_{\nu_1}^{\nu_2} \frac{\nu' k(\nu')}{\nu'^2 - \nu^2} d\nu'
\]
discretized as

\[
I_i = n_0 + 2/\pi \times 2h \times \sum_j f_j,
\]
where
\[
f_j = 0.5*k_j (\frac{1}{\nu_j - \nu_i} + \frac{1}{\nu_j + \nu_i})
\]

dispersive and dissipative mode, sum rules given. \cite{King1979}
\[
F(\omega) = \frac{\log r(\omega)}{\omega + i\omega'}
\]

@@

A systematic study of optical and electrical properties of \ce{WO3} thin film.\cite{Deb1973} Film density 6.5 \si{g\per cm^3}, substantial porosity. \ce{WO3} becomes substoichiometric at 1300-1500 K, and evaporate at a composition near \ce{WO_{2.96}}. $K \propto (h\nu - E_g)^2/h\nu$, indicating an allowed band to band transition, and 3.25 eV energy gap determined thereby. Refractive index $\epsilon_{st}$ of thin film \ce{WO3} found at 2.2, lower than that of single crystal value of 2.5; $n$ increases to 4.0 at absorption edge region, with $\alpha$ as high as $10^5$ \si{cm^{-1}}. So the color center can form in a thin layer of 100 nm; its density estimated by the Smakula's Equation:
\[
Nf = 0.89\times10^17\frac{n}{(n^2+2)^2} \alpha d
\]
where $f$ osc strength, n ref index, $\alpha$ in \si{cm^{-1}}, and d is the half width of absorption band. Assuming $f$ = 1, N to be $5\times10^{19}$ \si{cm^3}. 
Narrow conduction band proposed to explain the high energy peak at 4.39 eV and 5.25 eV. Impurity band when the ele wavefuntion overlap, the color center spacing comparable to lattice constant.

polycrystalline \ce{WO3} film reflectivity in NIR.\cite{Goldner1983} tentatively,  $E_p$ 4.07 eV was obtained by $R$ fitting using Drude model.

T and R data on ECD. \cite{OBrien1999}

ECD wo3 NW for fast response time. \cite{Liao2006a}

exhibits electrochromic functionality. reversible, recoverable, electrochromism, 
coloration efficiency, the doping amount, 
ion mobility is the bottleneck, 
The optical properties modification in EC materials is related to the electron density difference.

@@

raman assign

\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Name & Raman Shift (\si{cm^{-1}}) &  Ref   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & &\\
\ce{Na5W14O44} & & this work\\
\bottomrule
\end{tabular}
Materials in solid state, 
vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}

@@

Delichere1988 coloured states

@@

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$ in unit of \si{\coulomb \per cm^2} during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

### 2014-10-24 misc/draft.tex
supporting info reading
misc works of paper reading, wo3 raman table etc

>>>>

\gls{tmo} are a group of functional materials whose bleaching-coloration status can be reversibly switched using a finite durance of low DC voltage (\textless 5 V). Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques.
